SBML L3 paper response to reviewers

### 2019-12-31 main.tex
Initial content from Dagmar and Sarah's google doc

\documentclass{article}
\usepackage[utf8]{inputenc}

\title{SBML L3 paper response to reviewers}
\author{Mike Hucka}
\date{December 2019}

\begin{document}

\maketitle

\section{Introduction}

>>>>

\documentclass[11pt]{mhletter}

\newcommand{\ui}[1]{\emph{\textbf{#1}}}

\begin{document}
\thispagestyle{empty}
\input{letterhead}

\hspace{4in}%

\vspace*{2ex}

\begin{flushleft}
Thomas Lemberger\\
Molecular Systems Biology\\
EMBO Press
\end{flushleft}

\setlength{\parskip}{0.7em}

Dear Thomas, and reviewers,

We thank you for reviewing our manuscript on SBML Level~3 and providing many thoughtful comments and suggestions.  They helped us improve the manuscript.  Below you will find a point-by-point explanation of our responses to the reviewer's points; in addition, we have include a separate document showing the detailed differences (generated with the help of latexdiff) between the manuscript of July 2019 and the new version.  The differences include additional corrections and updates beyond the changes in response to the reviewer comments.

To the extent possible, we have endeavored to address all of the issues.  We hope that the reviewer's concerns have been addressed adequately and that the manuscript is now ready for publication.

% Ordering of signing authors is based on # of tasks assigned in the
% Google tracker document.
% MH: 6
% SK: 4
% DW: 4
% MK: 3
% CC: 2
% AD: 2
% FZ: 1
% CM: 1

With kind regards,\\
Michael Hucka, Dagmar Waltemath, Sarah Keating, Matthias K\"{o}nig, Claudine Chaouiya, Andreas Dr\"{a}ger, Fengkai Zhang, and Chris Myers, on behalf of all the coauthors.

\vspace*{2em}

\textbf{\underline{Reviewer \#1}}

\textbf{\textit{1. When reading the title, the introduction of a newly developed format is expected. The abstract also gives the impression as if the manuscript would describe a recent development. However, on page 3 (lines 38-39) it is stated that SBML Level 3 was released in 2010 (and published in 2015?). To prevent such a misunderstanding, it would be better to rephrase title and abstract.}}

\textbf{\textit{2. The only new features of SBML Level 3 compared to previous levels that are discussed are the modularity comprising packages. Is this the only relevant feature that has been introduced?}}

\textbf{\textit{3. While the development of SBML is indeed a success story, the manuscript's tone tends to be overenthusiastic and to gloss over difficulties or problems. Are there alternative standards? How frequently refuse researchers to provide SBML files for their models? How is the support by journals (probably favorable, but this should be discussed)?}}

\textbf{\textit{Minor point: the individual parts of the manuscript, while well written, could be better connected.}}

To help connect the sections better, we have expanded the final paragraph in the introduction to provide a preview of the remaining sections, and then in other places, we added phrases referencing different sections in order to try to connect the sections better.

\clearpage
\textbf{\underline{Reviewer \#2}}

\textbf{\textit{1. When/why is standardization beneficial?}}

\textbf{\textit{2. Costs/benefits of the standardization process.}}

\textbf{\textit{3. The value of SBML as a technical platform vs.\ as a governing body.}}

\textbf{\textit{4. Human readability/usability of SBML.}}

\textbf{\textit{5. SBML as a knowledge representation vs. a model implementation.}}

\textbf{\textit{Minor comments.}}

We have updated the text to address the minor comments.
